An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-08-06 poly-embed-journal/poly-embed-journal.tex
lovasz tightness proof

In light of this negative result, together with the fact that every polyhedral surrogate embeds some target loss (Theorem~\ref{thm:poly-embeds-discrete}), we now turn to the question: what target problem, then, \emph{is} the Lov\'asz hinge consistent for?
We show in \S~\ref{app:lovasz} that the answer is a variant of abstain loss where one can abstain on a set of labels $B\subseteq[k]$.
Recall that the symmetric difference is defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
\begin{theorem}\label{thm:lovasz-embed-main}
	Let $\hat\ell^f:\hat\R\times\Y\to\reals_+$, where $\hat\R = \{(A,B) \in 2^{[k]} \times 2^{[k]}: A\cap B=\emptyset\}$, be given by
	\begin{equation}
	\hat\ell^f((A,B))_S = f(A\triangle S\setminus B) + f(A\triangle S\cup B)~.
	\end{equation}
	Then the Lov\'asz hinge $L^f$ embeds $\hat\ell^f$.
  Moreover, the embedding is tight whenever $f$ is strictly submodular.
\end{theorem}
\raf{Something about how this could actually be a useful target and surrogate, provided you actually link from the surrogate to the target and not ignore $B$.}

@@

A set function $f:2^N\to\reals$ is \emph{submodular} if for all $S,T\subseteq N$ we have $f(S) + f(T) \geq f(S\cup T) + f(S\cap T)$.
A function is \emph{supermodular} if the inequality is reversed, and \emph{modular} if it holds with equality, for all $S,T\subseteq N$.
The function $f$ is \emph{increasing} if we have $f(S\cup T) \geq f(S)$, again for all $S,T\subseteq N$.

We are interested in convex surrogates for the following discrete loss $\ell:\R\times\Y\to\reals$, where $\R=\Y=2^N$,
\begin{equation}
\label{eq:discrete-set-loss}
\ell^f(A,S) = f(A\triangle S)~,
\end{equation}
where $\triangle$ is the symmetric difference operator, defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
Note: throughout we assume $\triangle$ has operator precedence over $\setminus$, $\cap$, and $\cup$.
In words, $\ell^f$ measures the joint error of our $k$ predictions by computing the set of mispredictions (elements in $A$ but not $S$ and vice versa) and calling the set function $f$.

@@

We have seen that the Lov\'asz hinge is consistent if and only if it is modular, as otherwise some report $(A,B)$ with $B\neq\emptyset$ is non-redundant.
\raft{Maybe we could do it this way to be more direct!}

>>>>

In light of this negative result, together with the fact that every polyhedral surrogate embeds some target loss (Theorem~\ref{thm:poly-embeds-discrete}), we now turn to the question: for what target problem \emph{is} the Lov\'asz hinge consistent?
We show in \S~\ref{app:lovasz} that the answer is a variant of abstain loss where one can abstain on a set of labels $B\subseteq[k]$.
Recall that the symmetric difference is defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
\begin{theorem}\label{thm:lovasz-embed-main}
	Let $\hat\ell^f:\hat\R\times\Y\to\reals_+$, where $\hat\R = \{(A,B) \in 2^{[k]} \times 2^{[k]}: A\cap B=\emptyset\}$, be given by
	\begin{equation}
	\hat\ell^f((A,B))_S = f(A\triangle S\setminus B) + f(A\triangle S\cup B)~.
	\end{equation}
	Then the Lov\'asz hinge $L^f$ embeds $\hat\ell^f$.
  Moreover, if $f$ is strictly submodular and strictly increasing, the embedding is tight.
\end{theorem}

While Theorem~\ref{thm:lovasz-consistent-main} shows that the Lov\'asz hinge is inconsistent, Theorem~\ref{thm:lovasz-embed-main} illuminates why: when there is sufficient uncertainty around some subset of labels, the loss encourages the learning algorithm to ``hedge'' and set prediction coordinates for that set equal to 0.
This observation reveals a potential peril of using the Lov\'asz hinge in noisy label settings.
On the other hand, of course, this revelation suggests a positive result as well: under an appropriate link from our construction in Theorem~\ref{thm:eps-thick-calibrated}\raft{Which theorem number to ref?}, the Lov\'asz hinge could be fruitfully applied to set-valued prediction problems when one allows the learning algorithm to abstain on a subset of labels.

@@

A set function $f:2^N\to\reals$ is \emph{submodular} if for all $S,T\subseteq N$ we have $f(S) + f(T) \geq f(S\cup T) + f(S\cap T)$.
If this inequality is strict whenever $S$ and $T$ are incomparable, meaning $S\not\subseteq T$ and $T\not\subseteq S$, then we say $f$ is \emph{strictly submodular}.
A function is \emph{modular} if the submodular inequality holds with equality for all $S,T\subseteq N$.
The function $f$ is \emph{increasing} if we have $f(S\cup T) \geq f(S)$ for all disjoint $S,T\subseteq N$, and \emph{strictly increasing} if the inequality is always tight.

Let $\triangle$ be the symmetric difference operator, defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
To avoid additional parentheses, throughout we assume $\triangle$ has operator precedence over $\setminus$, $\cap$, and $\cup$.

We are interested in convex surrogates for the following discrete loss $\ell^f:\R\times\Y\to\reals$, with $\R=\Y=2^N$,
\begin{equation}
\label{eq:discrete-set-loss}
\ell^f(A,S) = f(A\triangle S)~.
\end{equation}
In words, $\ell^f$ measures the joint error of our $k$ predictions by computing the set of mispredictions (elements in $A$ but not $S$ and vice versa) and calling the set function $f$.

@@

Finally, we show a sufficient condition for when the embedding is tight.
It appears from the proof that both assumptions on $f$ are required, though we leave open whether that is indeed the case.

\begin{lemma}
  Let $X,Y,Z\subseteq N$ such that $Y\cap Z = \emptyset$.
  Then $X\triangle (Y\cup Z) = X\triangle Y \triangle Z$.
\end{lemma}
\begin{proof}
  $X\triangle (Y\cup Z) = X\cup (Y\cup Z) \setminus (X \cap (Y\cup Z))$

  $X\triangle (Y\cup Z) = (X \setminus (Y\cup Z)) \cup ((Y\cup Z) \setminus X)$
\end{proof}

\begin{theorem}\label{thm:lovasz-embed-tight}
  Let $f$ be strictly submodular and strictly increasing.
  Then $L^f$ tightly embeds $\hat\ell^f$.
\end{theorem}
\begin{proof}
  Let $A,B\subseteq N$ be disjoint.
  We will show that $(A,B)$ is the unique $\hat\ell^f$-optimal report for the distribution $p$ given by
  \begin{equation}
    \label{eq:1}
    p(S) =
    \begin{cases}
      2^{-|B|} & S\setminus A \subseteq B \\
      0 & \text{otherwise}
    \end{cases}~.
  \end{equation}
  The condition $S\setminus A \subseteq B$ is equivalent to the existence of some $T\subseteq B$ such that $S = A \cup T$, and this $T$ must be disjoint from $A$ as $B$ is.
  The expected loss for $(A,B)$ under $p$ is therefore
  \begin{align*}
    \hat\ell^f((A,B);p)
    &= \sum_{T\subseteq B} 2^{-|B|} f(A\triangle (A\cup T)\setminus B) + f(A\triangle (A\cup T)\cup B)
    \\
    &= 2^{-|B|} \sum_{T\subseteq B} f(T\setminus B) + f(T\cup B)
    \\
    &= f(\emptyset) + f(B)~.
  \end{align*}

  Now suppose $A',B'\subseteq N$ are disjoint, with $(A',B') \neq (A,B)$.
  Once again we write the expected loss under $p$.
  We will use the observation that, as $A$ and $T$ are disjoint, $A\cup T = A\triangle T$.
  Defining $\hat A = A' \triangle A$, and using the associativity of $\triangle$, we then have $A' \triangle (A\cup T) = \hat A \triangle T$.
  \begin{align*}
    \hat\ell^f((A',B');p)
    &= 2^{-|B|} \sum_{T\subseteq B} f(A'\triangle (A\cup T)\setminus B') + f(A'\triangle (A\cup T)\cup B')
    \\
    &= 2^{-|B|} \sum_{T\subseteq B} f(\hat A\triangle T\setminus B') + f(\hat A\triangle T\cup B')
    \\
    &= \frac 1 2 \; 2^{-|B|} \sum_{T\subseteq B} \biggl( f(\hat A\triangle T\setminus B') + f(\hat A\triangle T\cup B')
    \\[-8pt]
    & \hspace*{85pt} + f(\hat A\triangle (B\setminus T)\setminus B') + f(\hat A\triangle (B\setminus T)\cup B') \biggr)~.
  \end{align*}

  We first suppose $B \subseteq B'$.
  Then $\hat A\triangle T\setminus B' = \hat A \setminus B'$ and $\hat A\triangle T\cup B' = \hat A\cup B'$ for any $T \subseteq B$.
  We conclude
  \begin{align*}
    \hat\ell^f((A',B');p)
    &= \frac 1 2 \; 2^{-|B|} \sum_{T\subseteq B} \biggl( f(\hat A\setminus B') + f(\hat A\cup B') + f(\hat A\setminus B') + f(\hat A\cup B') \biggr)
    \\
    &= f(\hat A\setminus B') + f(\hat A\cup B')~.
  \end{align*}
  We will show either (i) $\hat A\setminus B' \neq \emptyset$ or (ii) $\hat A\cup B' \supsetneq B$ hold, and then apply the fact that $f$ is strictly increasing.
  If (ii) fails, since $B \subseteq B'$, we must have $B = B'$.
  Then $B = B'$ is disjoint from both $A$ and $A'$, and therefore from $\hat A = A'\triangle A$.
  We therefore have $\hat A\setminus B' \neq \emptyset \iff \hat A \neq \emptyset \iff A \neq A'$, which must hold as $B = B'$ yet $(A,B) \neq (A',B')$ by assumption.
  Thus, at least (i) or (ii) hold.
  As $f$ is strictly increasing, we conclude $\hat\ell^f((A',B');p) > f(\emptyset) + f(B) = \hat\ell^f((A,B);p)$.

  Now suppose $B \not\subseteq B'$.
  We claim that there exists $T\subseteq B$ such that one of the following two cases hold:
  \begin{enumerate}
  \item[(i)]
    $\hat A\triangle T\setminus B'$ and 
    $\hat A\triangle (B\setminus T)\cup B'$
    are incomparable;
  \item[(ii)]
    $\hat A\triangle T\cup B'$
    and
    $\hat A\triangle (B\setminus T)\setminus B'$
    are incomparable. 
  \end{enumerate}
  We will then apply strict submodularity to conclude.

  \bigskip
  Take $T = B\setminus B'$.

  If $B' = \emptyset$

\raf{It seems we need to handle the case where $B\setminus B'$ is a singleton, since then we run into the same problem as when we used only $\emptyset$ and $B$.  If larger, we can take $T$ to fragment $B\setminus B'$ and I think we're good...}

  Let $i\in B\setminus B'$.
  If $i\in A'$, then $i\in\hat A$ (as $i\notin A$).

  \bigskip
  For case (i),
